R Notebook

### 2022-02-10 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.9.22
Spin up the FML Drive!!!

Getting into the hard part of creating network data

FORMATING SOURCE DATA

# DATA Cleaning
-   rename column names to something memorable
```{r Rename columns}

   # Rename column names

names(smugDnkIdx_df)[1] <- "Drink_Name"
names(smugDnkIdx_df)[2] <- "Ingredient"
names(smugDnkIdx_df)[3] <- "Ingredient_ClassType"
names(smugDnkIdx_df)[4] <- "Drink_Code"

```
-   Drop rows without values 
```{r Remove missing values}

#One-column based criteria: Extract rows where

testData <- smugDnkIdx_df

testData  %>% filter(is.na(Drink_Code))

@@

-   Col X5
    Drop All together
    split varriables into new columns

#
## 1.  *Identify and describe content of nodes and
    links,*

@@

##2.  *Identify format of data set (i.e., matrix or
    edgelist, directed or not, weighted or not),
    and*

>>>>

```{r}

colnames(smugDnkIdx_df)

head(smugDnkIdx_df, n=10)

head(smugDnkIdx_df, n=10)

@@

> dim() smugDnkIdx_df
>
> rows: 785
>
> columns: 4
>
> column names: "X2" "X3" "X5" "X6"

-   *need to rename column names to something
    memorable*

    ```{r}

    # example of melt function
    library(reshape)

    mdata <- 
      melt(smugDnkIdx_df,
           id=c(
             "id",
             "time")
           )
    ```

1.  *Identify and describe content of nodes and
    links,*

@@

2.  *Identify format of data set (i.e., matrix or
    edgelist, directed or not, weighted or not),
    and*
